Measurement and Probability in Fuzzy Quantum Theories

### 2016-11-26 proposal/prop.tex
inputenc
proposal\prop.tex Add citations...

\documentclass{article}
\usepackage[ backend=biber]{biblatex}
\addbibresource{prop.bib}
\ExecuteBibliographyOptions{sorting=none,maxbibnames=5,doi=false,isbn=false,url=false}
\usepackage{fullpage}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage{tensor}
\usepackage{url}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{mathrsfs}
\usepackage{bbm}
\usepackage{bbold}
\usepackage{wesa}
\usepackage{graphicx}

@@

We will begin by reviewing existing work that recasts classical
probability spaces in a resource-aware setting and move to our
proposal which, briefly speaking, aims at recasting quantum
probability and hence quantum measurement to a corresponding
resource-aware setting. In particular, we plan on addressing the
Meyer-Mermin debate~\cite{PhysRevLett.83.3751, Mermin1999,
  BarrettKent2004} on the impact of finite precision measurements on
the relevance of the Kochen-Specker theorem. We argue that no matter
what the results are their impact will be strong. Positive results
that formulate a computable, with clear resource bounds, theory of
quantum measurement and quantum probability would be essential for
understanding and realizing quantum computation. Any negative results
would redirect research that aims at realizing quantum computation to
other approaches. At an intellectual level, the results will solve or
clarify several paradoxes in quantum mechanics, quantum information,
computability, and complexity theory.

@@

The conventional definition of a probability space builds upon the
field of real numbers. In more detail, a probability space consists of
a \emph{sample space} $\Omega$, a space of \emph{events}~$\events$,
and a \emph{probability measure}~$\pmeas$ mapping events in $\events$
to the real interval $[0,1]$. We will only consider \emph{finite} sets
of events and restrict our attention to non-empty finite sets $\Omega$
as the sample space. The space of events $\events$ includes every
possible subset of $\Omega$: it is the
powerset~$2^{\Omega}=\left\{ E ~\middle|~ E\subseteq\Omega\right\}
$.
For future reference, we emphasize that events are the primary notion
of interest and that the sample space is a convenient artifact that
allows us to treat events as sets obeying the laws of Boolean algebra.

@@

\noindent It is useful to think that this probability measure is
completely determined by the ``reality'' of the two coins in question
and their characteristics, in the sense that each pair of coins
induces a measure, and each measure must correspond to some pair of
coins. The measure above would be induced by two particular coins such
that the first coin is twice as likely to land tails up than heads up
and the second coin is double-headed. In a strict computational
or experimental setting, one should question the reliance of the
definition of probability space on the uncountable and uncomputable
real interval $[0,1]$. This interval includes numbers like
$0.h_{1}h_{2}h_{3}\ldots$ where $h_{i}$ is 1 or 0 depending on whether
Turing machine $M_{i}$ halts or not. Such numbers cannot be
computed. This interval also includes numbers like $\frac{\pi}{4}$
which can only be computed with increasingly large resources as the
precision increases. Therefore, in a resource-aware computational or
experimental setting, it is more appropriate to consider probability
measures that map events to a set of elements computable with a fixed
set of resources. We expand on this observation in the next section
and then recall its formalization using interval-valued probability
measures~\cite{Weichselberger2000,JamisonLodwick2004}.

@@

The early formalization of the process of computing using Turing
machines~\cite{citeulike:321509} or the
$\lambda$-calculus~\cite{Barendregt:Lambda} viewed a computation as
realizing a mathematical function. From our perspective, the most
important consequence of this view is that the properties of the
computed function existed independently of any observation,
calculation, or interaction. For example, a function is
\emph{injective} or not independently of any observation. An agent can
only interact with the computation by asking questions regarding its
input-output behavior and although such interaction would reveal
fragments of the computed function and its innate properties it could
not change it or affect it in any way.

>>>>

\documentclass{article}
\usepackage[ backend=biber]{biblatex}
\addbibresource{prop.bib}
\ExecuteBibliographyOptions{sorting=none,maxbibnames=5,doi=false,isbn=false,url=false}
\usepackage{fullpage}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{tensor}
\usepackage{url}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{mathrsfs}
\usepackage{bbm}
\usepackage{bbold}
\usepackage{wesa}
\usepackage{graphicx}

@@

We will begin by reviewing existing work that recasts classical
probability spaces in a resource-aware setting and move to our
proposal which, briefly speaking, aims at recasting quantum
probability and hence quantum measurement to a corresponding
resource-aware setting. In particular, we plan on addressing the
Meyer-Mermin debate~\cite{PhysRevLett.83.3751, Mermin1999,
  BarrettKent2004} on the impact of finite precision measurements on
the relevance of the Kochen-Specker
theorem~\cite{kochenspecker1967,Redhead1987-REDINA,peres1995quantum,Jaeger2007}.
We argue that no matter
what the results are their impact will be strong. Positive results
that formulate a computable, with clear resource bounds, theory of
quantum measurement and quantum probability would be essential for
understanding and realizing quantum computation. Any negative results
would redirect research that aims at realizing quantum computation to
other approaches. At an intellectual level, the results will solve or
clarify several paradoxes in quantum mechanics, quantum information,
computability, and complexity theory.

@@

The conventional definition of a probability space builds upon the
field of real numbers. In more detail, a probability space consists of
a \emph{sample space} $\Omega$, a space of \emph{events}~$\events$,
and a \emph{probability measure}~$\pmeas$ mapping events in $\events$
to the real interval $[0,1]$. We will only consider \emph{finite} sets
of events and restrict our attention to non-empty finite sets $\Omega$
as the sample space. The space of events $\events$ includes every
possible subset of $\Omega$: it is the
powerset~$2^{\Omega}=\left\{ E ~\middle|~ E\subseteq\Omega\right\}
$.
For future reference, we emphasize that events are the primary notion
of interest and that the sample space is a convenient artifact that
allows us to treat events as sets obeying the laws of Boolean
algebra~\cite{Boole1948,Redhead1987-REDINA,Griffiths2003}.

@@

\noindent It is useful to think that this probability measure is
completely determined by the ``reality'' of the two coins in question
and their characteristics, in the sense that each pair of coins
induces a measure, and each measure must correspond to some pair of
coins. The measure above would be induced by two particular coins such
that the first coin is twice as likely to land tails up than heads up
and the second coin is double-headed. In a strict computational
or experimental setting, one should question the reliance of the
definition of probability space on the uncountable and
uncomputable~\cite{Turing01011937,Ziegler2007,weihrauch2012computable}
real interval $[0,1]$. This interval includes numbers like
$0.h_{1}h_{2}h_{3}\ldots$ where $h_{i}$ is 1 or 0 depending on whether
Turing machine $M_{i}$ halts or not. Such numbers cannot be
computed. This interval also includes numbers like $\frac{\pi}{4}$
which can only be computed with increasingly large resources as the
precision increases. Therefore, in a resource-aware computational or
experimental setting, it is more appropriate to consider probability
measures that map events to a set of elements computable with a fixed
set of resources. We expand on this observation in the next section
and then recall its formalization using interval-valued probability
measures~\cite{Weichselberger2000,JamisonLodwick2004}.

@@

The early formalization of the process of computing using Turing
machines~\cite{Turing01011937} or the
$\lambda$-calculus~\cite{Barendregt:Lambda} viewed a computation as
realizing a mathematical function. From our perspective, the most
important consequence of this view is that the properties of the
computed function existed independently of any observation,
calculation, or interaction. For example, a function is
\emph{injective} or not independently of any observation. An agent can
only interact with the computation by asking questions regarding its
input-output behavior and although such interaction would reveal
fragments of the computed function and its innate properties it could
not change it or affect it in any way.
